SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-27 paper.tex
new research problem (RP5)

@@

>>>>

\textcolor{blue}{\textbf{(RP5)} provide tools and approaches capable of addressing different software languages and application interfaces, with the goal of reducing the time needed to adapt current verification techniques to new developments and technologies.}

@@

\textcolor{blue}{\textbf{(RP5)} Although ESMBMC \cite{Cordeiro12} was extended to support C/C++ and some variants, new application interfaces and languages are often developed, which then claim for suitable verification tools. Indeed, it would be interesting if one needed only to load a new language model, which along with a BMC core could check new programs. Some work towards that was already presented by Sousa, Cordeiro, and Filho, which employed operational models  for checking Qt-based programs. In summary, the BMC core (in that case, ESBMC) is not changed, but instead an operation model, which implements the behavior and features of Qt libraries, is used for providing the code structure to be checked. Such research problem is closely related to the first one (\textbf{(RP1)}) and has the potential to devise a new paradigm in software verification.}
